### 2014-11-13 tex/intro.tex
minor changes to intro

In recent years symbolic execution has provided the basis for various 
software testing and analysis techniques. Symbolic execution
systematically explores the program execution space using
symbolic input values, and for each explored path, computes
constraints on the symbolic inputs to create a \emph{ path condition}.
The set of path conditions computed by
symbolic execution characterize the observed program execution
behaviours and have been used as an enabling technology for various
applications, e.g., regression
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
data structure repair~\cite{KhurshidETAL05RepairingStructurally},
dynamic discovery of
invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
debugging~\cite{Ma:2011}.

@@

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. Our
inspiration is found in the domain of static analysis that uses sets
of constraints over heap locations to encode multiple heaps in a
single representation. These sets, sometimes known as \emph{value
  sets} or \emph{value summaries}, allow multiple heaps to be
represented simultaneously with a higher degree of precision than
afforded by traditional techniques for shape analysis. Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{Xie:2005}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static analysis, over
approximation of the heap representations alleviates some of these
limitations but also leads to false positives. Also, updates to heaps
require a rewrite of the constraint system making it prohibtive for use
in the context of symbolic execution.

@@

In this work, to effectively represent multiple heaps simultaneously
in the context of symbolic execution we define a novel heap
representation and an algorithm to initialize and update the heap
on-the-fly. Our summary heap approach supports aliasing, does not
require constraint rewriting on heap updates, and reduces
non-determinism in the search space during symbolic execution.

We represent the heap as a bipartite graph consisting of references
and locations. Each reference is able to point to multiple locations,
where each edge is predicated on constraints over aliasing between
references. Each location points to a single reference for a given
field. The use of a bipartite graph affords two key advantages: (i)
it allows for a non-recursive definition of objects which enables us
to support aliasing, and (ii) it does not introduce auxiliary variables or 
require rewriting non-local constraints during updates to the heap.

@@

The summary heap algorithm is sound and complete with
respect to properties that are provable using GSE. This proof is
accomplished by showing the existence of a bisimulation relation
between states in GSE and states in the summary heap algorithm. In
practical terms, any property that can be proved using GSE can also be
proved using summary heaps, furthermore, any property proved by
summary heaps can also be proved by GSE. Of course, both require a
bound on heap reference chains and loops.

@@

A preliminary implementation in Java Pathfinder (JPF) shows that in
general, that the heap summary algorithm improves over other
state-of-the-art techniques, and in some instances, the improvement is
remarkable: two-orders of magnitude reduction in running time. More
critically though, the heap summary enables the initialization of
larger more complex heaps than heretofore possible as shown in our
results.

@@

\item\textbf{-} A proof-of-concept implementation and small empirical study 
demonstrating the scalability of the heap summary approach
  compared to other GSE approaches.

>>>>

In recent years symbolic execution has provided the basis for various 
software testing and analysis techniques. Symbolic execution
systematically explores the program execution space using
symbolic input values, and for each explored path, computes
constraints on the symbolic inputs to create a \emph{ path condition}.
The path conditions computed by
symbolic execution characterize the observed program execution
behaviours and have been used as an enabling technology for various
applications, e.g., regression
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
data structure repair~\cite{KhurshidETAL05RepairingStructurally},
dynamic discovery of
invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
debugging~\cite{Ma:2011}.

@@

The goal of this work is to mitigate the state space explosion problem
in GSE by grouping multiple heaps together and only partitioning the
heaps at points of divergence in the control flow graph. Our
inspiration is found in the domain of static analysis that uses sets
of constraints over heap locations to encode multiple heaps in a
single representation. These sets, sometimes known as \emph{value
  sets} or \emph{value summaries}, allow multiple heaps to be
represented simultaneously with a higher degree of precision than
afforded by traditional techniques for shape analysis. Some of these
previous attempts, however, are unable to handle aliasing in heaps due
to a recursive definition of objects~\cite{Xie:2005}, while others require a
set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static analysis, over
approximation of the heap representations alleviates some of these
limitations but also leads to infeasible heaps. Also, heap updates
require a rewrite of the constraint system making it prohibtive for use
in the context of symbolic execution.

@@

In this work, to effectively represent multiple heaps simultaneously
in the context of symbolic execution, we define a novel heap
representation and an algorithm to initialize and update the heap
on-the-fly. Our summary heap approach supports aliasing, does not
require constraint rewriting on heap updates, and reduces
non-determinism in the search space during symbolic execution.

We represent the heap as a bipartite graph consisting of references
and locations. Each reference is able to point to multiple locations,
where each edge is predicated on constraints over aliasing between
references. Each location points to a single reference for a given
field. The use of a bipartite graph affords two key advantages: (i)
it allows for a non-recursive definition of objects which enables us
to support aliasing, and (ii) it does not introduce auxiliary variables or 
require rewriting of non-local constraints during updates to the heap.

@@

This combination of summary heap and lazy initialization
enable us to improve the efficiency of symbolic execution of heap
manipulating programs over state-of-the-art techniques.
Furthermore, the summary heap algorithm is sound and complete with
respect to properties that are provable using GSE. This proof is
accomplished by showing the existence of a bisimulation relation
between states in GSE and states in the summary heap algorithm. In
practical terms, any property that can be proved using GSE can also be
proved using summary heaps, and, any property proved by
summary heaps can also be proved by GSE. Of course, both require a
bound on heap reference chains and loops.

@@

A preliminary implementation in Java Pathfinder (JPF) shows that in
general, that the heap summary algorithm improves over other
state-of-the-art techniques, and in some instances, the improvement is
remarkable: two-orders of magnitude reduction in running time. More
critically though, the heap summary enables the initialization of
larger more complex heaps than previously possible as shown in our
results.

@@

\item\textbf{-} A proof-of-concept implementation and empirical study 
demonstrating the scalability of the summary heap approach
compared to other GSE approaches.
